\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-10-19 demystify.tex

So what can you do about this? several things including asking your CS dept to put itself on CSRankings (it's the easiest way to get CS people to know about the school) and explaining about your school in your statement (ask your LOR writer to do that too). Of course, if you're interested in working with Vietnamese, consider  \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{CS PhD programs in the US that have Vietnamese professors}.

% \begin{commentbox}[Hung:]
% I personally don’t care about which schools students attended. There are many other ways to evaluate an applicant.
% \end{commentbox}

>>>>

So what can you do about this? several things including asking your CS dept to put itself on CSRankings (it's the easiest way to get CS people to know about the school and its CS faculty)  and explaining about your school in your statement (ask your LOR writer to do that too). Of course, if you're interested in working with Vietnamese, consider  \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{CS PhD programs in the US that have Vietnamese professors}.
